Universal Anonymous Signatures

### 2022-08-12 prism-backend/research/gsac/app-related-proofs.tex
Updating proofs of UAS => MPS

\begin{theorem}[Anonymity of \CUASAC]
  \label{thm:anon-cuasac}
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
  according to \cite{fhs19}.
\end{theorem}

@@

We prove that \CUASRAC is an anonymous and unforgeable anonymous credential
scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
is anonymous and has unforgeable signing. Note that issuance unforgeability
of \CUASGen is not needed, as the model in \cite{fhs19} does not allow
leveraging other credentials not any fixed custom issuance policy. Thus,
signature unforgeability from \UAS is enough. Note that AC schemes modelled
as in \cite{fhs19} do not have issuance anonymity, as the user public key
is passed to the issuer.

\begin{theorem}[Anonymity of \CUASRAC]
  \label{thm:anon-cuasrac}
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, and $F$ is one-way and collision-resistant,
  then \CUASAC is an anonymous AC scheme according to \cite{fhs19}.
\end{theorem}

@@

  First observe that, given a revocation handle $F(V,id)$ extracted from any
  credential showing, it is not possible to extract $id$, as $F$ is one-way
  and collision-resistant.

  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR,ReqCredHandle$, \advB
  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, of \OPEN respectively.
  Note that ``translating'' the inputs from the former into inputs for the
  latter is trivial. Also, observe that $ReqCredHandle$ essentially refuses to
  open transcripts from challenge users (signatures, in the non-interactive
  equivalent), as $F(V,\attrs_1(\ccid_0) \neq F(V,\attrs_1(\ccid_1)$ with
  overwhelming probability (see the $\tyinsp \neq \yinsp$) check in
  \figref{fig:oracles2}. Obviously, if \adv~ wins in its anonymity game, then
  so does \advB with the same probability.
  % 
  \qed
\end{proof}

\begin{theorem}[Unforgeability of \CUASRAC]
  If the base \CUASGen construction has sign unforgeability according to
  \defref{def:sign-forge-uas}, and $F$ is one-way and collision-resistant, then
  \CUASRAC is an unforgeable RAC scheme.
\end{theorem}

\begin{proof}
  Given \adv~ against unforgeability of \CUASRAC as defined in
  \figref{fig:model-rac}, we build an adversary \advB against sign
  unforgeability of \CUASGen as defined in \defref{def:sign-forge-uas}.

  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
  that \adv~ wins its game via the winning condition of line 6 in the RAC
  unforgeability game. The same reasoning as in \CUASAC applies here. Next, note
  that the probability of \adv~ winning its game via the winning condition at
  line 9 is negligible, due to soundness of the NIZK scheme used for signing,
  and the one-wayness and collision-resistance of $F$ in
  $\feval^{\dattrs,F,V,L}$ and $\finsp^{F}$.
  % 
  \qed
\end{proof}

@@

As stated, we restrict to privacy-1 of MPS. Unforgeability-1 in MPS is
equivalent to sign unforgeability in \UAS. Unforgeability-2 in MPS is
equivalent to non-frameability in \UAS. Finally note that, in UAS, we do not
explicitly model extractability, but rather make it an inherent requirement in
the unforgeability and non-frameability definitions. Thus, our \CUASMPS
construction also ensures MPS-extractability.

@@

\begin{proof}
  The proof is direct, by observing that the models are equivalent.

  First, note that, in MPS the adversary is required to output a function $F$,
  challenge message, and a pair of user secret keys and witnesses (in \UAS, the
  witnesses are the credentials). This is precisely what \CHALb requires as
  input in our \UAS modelling.

  Next, in MPS, validity of the output of $F$ is checked. In MPS, this
  translates to checking that $F$ does not ouptut $0$. In UAS, this is checked
  in the \SIGN and \CHALb oracles, which abort if the output produced by \feval
  does not belong in \rngfeval -- a well defined set of acceptable outputs by
  the chosen \feval.

  The MPS adversary is then allowed to make more oracle queries, and outputs a
  response bit. Just as in \UAS. Thus, if \CUASMPS satisfies signature
  anonymity, it is also an MPS scheme satisfying privacy-1.  
  % 
  \qed
\end{proof}

\begin{theorem}[Extractability of \CUASMPS]
  If the base \CUASGen construction has signature unforgeability according to
  \defref{def:sign-forge-uas}, then it is an extractable MPS scheme.
\end{theorem}

\begin{proof}
  The proof is direct, as the conditions checked in the extractability
  experiment in MPS are also checked in the signature unforgeability experiment
  for \UAS.

  Concretely, \Verify must accept the signature, and the ouptut of \feval and
  \finsp, computed with the values extracted by \ExtractSign, must respectively
  match those output by the adversary (for \feval), and computed honestly by the
  signature unforgeability (for \finsp).  
  \qed
\end{proof}

\begin{theorem}[Unforgeability-1 of \CUASMPS]
  If the base \CUASGen construction has signature unforgeability according to
  \defref{def:sign-forge-uas}, then \CUASMPS satisfies unforgeability-1 as
  defined in \cite{ngsy22}.
\end{theorem}

\begin{proof}
  For an MPS scheme to satisfy type-1 unforgeability, it has to be extractable.
  This is directly satisfied by signature unforgeability in \UAS.
  %
  Next, the adversary wins in the unforgeability-1 MPS experiment if it manages
  to produce a signature that has not been produced via a call to their \SIGN
  oracle, nor it can be associated to an corrupt user. Indeed, if that happens,
  then such adversary can be used to build an adversary winning the signature
  unforgeability game against \CUASMPS, through winning condition at line 12 --
  as \IdentifySig does not return 1 for any known \uid. Thus, if \CUASMPS has
  signature unforgeability, it also satisfies unforgeability-1 of MPS schemes.
  %
  \qed
\end{proof}

@@

\begin{proof}
  For an MPS scheme to have type-2 unforgeability, it has to be extractable.
  This is directly satisfied by non-frameability in UAS (a similar reasoning
  as for signature unforgeability and extractability applies here).
  %
  Next, in MPS, the adversary wins if the produced signature has not been
  output by the \SIGN oracle, but Extract outputs the identifier of an honest
  user. This is the same check done in lines 9 and 10 of the non-frameability
  game in \UAS. Therefore, if \CUASMPS satisfies non-frameability as defined in
  \defref{def:frame-uas}, it also satisfies type-2 unforgeability in MPS.
  \qed
\end{proof}

>>>>

\begin{theorem}[Anonymity of \CUASAC]
  \label{thm:anon-cuasac}
  If the base \CUASGen construction is anonymous according to
  \defref{def:anonymity-uas}, then \CUASAC is an anonymous AC scheme according
  to \cite{fhs19}.
\end{theorem}

@@

We prove that \CUASRAC is an anonymous and unforgeable anonymous credential
scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
has signature anonymity and is unforgeable.

\begin{theorem}[Anonymity of \CUASRAC]
  \label{thm:anon-cuasrac}
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, and $F$ is one-way, then \CUASAC is an
  anonymous AC scheme according to \cite{fhs19}.
\end{theorem}

@@

  First observe that, given a revocation handles $F(V,\cidi)$ and $F(V,\cidu)$
  extracted from any credential showing, it is not possible to extract $\cidi$
  nor $\cidu$, as $F$ is one-way.

  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR,ReqCredHandle$, \advB
  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, or \OPEN, respectively.
  Note that ``translating'' the inputs from the former into inputs for the
  latter is trivial. Also, observe that $ReqCredHandle$/\OPEN essentially
  refuses to open transcripts from challenge users (signatures, in the
  non-interactive equivalent), as $F(V,\ccidi_0) \neq F(V,\ccidi_1)$ (and,
  similarly, for $\ccidu_b$) with overwhelming probability (see the $\tyinsp
  \neq \yinsp$) check in \figref{fig:oracles2}. Obviously, if \adv~wins in its
  anonymity game, then so does \advB with the same probability.
  % 
  \qed
\end{proof}

\begin{theorem}[Unforgeability of \CUASRAC]
  If the base \CUASGen construction has unforgeability according to
  \defref{def:forge-uas}, and $F$ is one-way, then
  \CUASRAC is an unforgeable RAC scheme.
\end{theorem}

\begin{proof}
  Given \adv~against unforgeability of \CUASRAC as defined in
  \figref{fig:model-rac}, we build an adversary \advB against unforgeability of
  \CUASGen as defined in \defref{def:forge-uas}.

  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
  that \adv~wins its game via the winning condition of line 7 in the RAC
  unforgeability game. The same reasoning as in \CUASAC applies here. Next, note
  that the probability of \adv~winning its game via the winning condition at
  line 9 is negligible, due to soundness of the NIZK scheme used for signing,
  and the one-wayness of $F$ in $\feval^{\dattrs,F,V,L}$ and $\finsp^{F}$.
  % 
  \qed
\end{proof}

@@

As stated, we restrict to privacy-1 of MPS (although, as discussed, we actually
achieve something slightly stronger). Unforgeability-1 in MPS is
implied by unforgeability in \UAS (where the latter also covers unforgeability
of \fissue evaluations, plus verifiable openings). Unforgeability-2 in MPS is
equivalent to non-frameability in \UAS (where the latter also includes
framing via verifiable openings). Finally note that, in UAS, we do not
explicitly model extractability, but rather make it an inherent requirement in
the unforgeability and non-frameability definitions. Thus, our \CUASMPS
construction also ensures MPS-extractability.

@@

\begin{proof}  
  Note that the privacy-1 game in MPS and the signature anonymity game in \UAS
  are, in essence, equivalent. Thus, given an adversary \adv~that breaks
  privacy-1 of \CUASMPS as defined for MPS, it is easy to build an adversary
  \advB breaking signature anonymity of the underlying \CUASGen, as defined in
  \UAS.

  \advB simply leverages its own oracles in order to answer oracle queries from
  \adv: $\mathcal{O}_{read},\mathcal{O}_{write},\mathcal{O}_{CU},\mathcal{O}_{HU},
  \mathcal{O}_{sig},\mathcal{O}_{open}$ in MPS correspond to \RREG, \WREG,
  \CUGEN, \HUGEN, \SIGN and \OPEN in \UAS, respectively. The output given by
  \adv~in the first stage of the MPS game is then directly used as input to
  \advB's \CHALb oracle. Finally, \advB outputs whatever \adv~outputs.

  Since the simulation is direct, it is easy to see that, whenever \adv~wins,
  so does \advB.
  % 
  \qed
\end{proof}

\begin{theorem}[Extractability of \CUASMPS]
  If the base \CUASGen construction has non-frameability according to
  \defref{def:frame-uas}, then \CUASMPS is an extractable MPS scheme.
\end{theorem}

\begin{proof}  
  The proof is direct, as the winning conditions in the extractability
  experiment in MPS are also winning conditions in the non-frameability
  experiment for \UAS. That is, an adversary \adv~against extractability of
  \CUASMPS, as defined in MPS, can be used to build an adversary \advB breaking
  non-frameability of \CUASGen, as defined in the \UAS model.

  \advB simulates \adv's game essentially as in the privacy-1 proof. Note also
  that \adv~receives the issuer's secret key. This can be obtained by \advB via
  its \ICORR oracle. Eventually, \adv~outputs a $(F,M,\Sigma)$ tuple, which
  corresponds to $(\feval^{g,MPS},\msg,\Sig)$ (with $g=F$ in MPS) in \CUASGen,
  which \advB outputs in its own game. In addition, \advB outputs as $(\yinsp,
  \pi)$ values the output of \Open over $(\Sig,\msg)$ -- which internally
  computes $\finsp^{h,MPS}$, for $h=G$ in MPS.
  % 
  Note that the $\feval^{g,MPS}$ and $\finsp^{h,MPS}$ functions in \CUASMPS
  mimic the behaviour of MPS's $F$ and $G$, respectively. Thus, if \adv wins
  because $F$ returns $0$ when evaluated on the extracted values, then \advB
  wins at line 7 of the non-frameability game, as a legitimately computed
  $\feval^{g,MSP}$ function cannot output $0$. Similarly, if \adv~wins because
  the value returned by an honestly computed open function over the adversarial
  $(F,M,\Sigma)$ tuple does not match the output of $G$ over the extracted
  values, \advB wins at line 9: note that \advB returns the \yinsp value that
  \Open outputs (when computed honestly over \adv's output), whereas
  $\finsp^{g,MSP}=G$; thus, if both values differ in \adv's game, then they also
  differ in \advB's game.
  %
  \qed
\end{proof}

\begin{theorem}[Unforgeability-1 of \CUASMPS]
  If the base \CUASGen construction is unforgeable according to
  \defref{def:forge-uas}, then \CUASMPS satisfies unforgeability-1 as defined in
  \cite{ngsy22}.
\end{theorem}

\begin{proof}
  Given an adversary \adv~against unforgeability-1 of \CUASMPS, as defined in
  the MPS model, we build \advB that breaks unforgeability of the underyling
  \CUASGen, as defined for \UAS.

  Simulation of \adv's oracles by \advB is again direct (as in previous proofs).
  Now, suppose that \adv~wins. Then, by assumption, the identity extracted by
  \adv~(which maps to a $\cid$ for \advB), does not belong to the set of corrupt
  users in \adv's game. By construction of \advB, then, $\OWNR[\cid] \notin \CU$
  in \advB's unforgeability game.
  \todo{The following seems wrong.}
  But it cannot belong to an honest user either,  
  as \adv's signature does not exist in \SIG. Otherwise, suppose it belongs to
  an honest user (in list \HU of \advB's game). Then, it breaks one-more
  unforgeability of the \SBCM scheme used by \CUASGen, as it is a valid.
  %
  \qed
\end{proof}

@@

\begin{proof}
  Given an adversary \adv~against unforgeability-2 of \CUASMPS, as defined in
  the MPS model, we build \advB that breaks non-frameability of the underyling
  \CUASGen, as defined for \UAS.

  Simulation of \adv's oracles by \advB is as in the unforgeability-1 proof.
  \advB outputs whatever \adv~outputs, adding a $(\yinsp,iproof)$ pair, honestly
  generated from \adv's output. Note that the winning condition of \adv~
  requires that the produced signature belongs to an honest user, without
  having been produced via a call to the signing oracle. By construction of
  \advB, this directly makes \advB win in line 11 of the non-frameability game.
  %
  \qed
\end{proof}

### 2022-08-12 prism-backend/research/gsac/app-uas-proofs.tex
Updating proofs of UAS => MPS

  \paragraph{(e) All {\cred}s are bound to the same \usk.} %
  $\NIZKRel^{\Sign}$ includes a condition that $\forall i\in[n],
  \SBCMVerify(\ipk_i,\cred_i,\usk,\attrs_i) = 1$. Thus, simulation
  extractability of $\NIZK^{\Sign}$ and correctness of \SBCM, ensure that all
  credentials involved in the signature contain the same \usk as their user key
  (first) attribute. Thus, either $\OWNR[\lbrace \cid_i \rbrace_{i\in[n]}]$
  returns some \uid in $\HU \cup \CU$, or it returns $\bot$ because no such
  \uid exists (but not because more than one \cid belongs to different {\uid}s).
  Assume that no such \uid exists. Such a signature breaks the one-more
  forgery property of \SBCM, as it has not been produced via a call to \SIGN
  (it is not in $\SIG$). Therefore, the probability that \adv~wins at line 14 is
  negligible, given simulation extractability of $\NIZK^{\Sign}$, and
  correctness and one-more forgery security of \SBCM.
  %
  \qed
\end{proof}

>>>>

  \paragraph{(e) All {\cred}s are bound to the same \usk.} %
  $\NIZKRel^{\Sign}$ includes a condition that $\forall i\in[n],
  \SBCMVerify(\ipk_i,\cred_i,\usk,\attrs_i) = 1$. Thus, simulation
  extractability of $\NIZK^{\Sign}$ and correctness of \SBCM, ensure that all
  credentials involved in the signature contain the same \usk as their user key
  (first) attribute. Thus, either $\OWNR[\lbrace \cid_i \rbrace_{i\in[n]}]$
  returns some \uid in $\HU \cup \CU$, or it returns $\bot$ because no such
  \uid exists (but not because more than one \cid belongs to different {\uid}s).
  Assume that no such \uid exists. Then, the {$\cred_i$}s extracted by
  \ExtractSign cannot have been produced via a call to either \OBTISS or \ISSUE,
  since they only accepts calls from known {\uid}s (either in \HU or \CU,
  respectively). Since, by simulation extractability of $\NIZK^{\Sign}$, at
  least one such credential must have been used to produce the signature, then
  this breaks the one-more forgery property of the underlying \SBCM.
  %
  \qed
\end{proof}

### 2022-08-12 prism-backend/research/gsac/formal-uas.tex
Updating proofs of UAS => MPS

\todo{Mention that, in this definition, a credential that does not meet \fissue
  is not considered a forgery unless it is used to produce a signature. This is
  consistent with other works -- e.g., Camenisch, Krenn, Lehmann...}

@@

\paragraph{On the generality of unforgeability in \UAS schemes.} %
Regarding the information revealed at signature time ($\yeval^0$), \UAS's
unforgeability notion is equivalent to that of known AC schemes. It is the
generalization of the information output at opening time ($\yinsp$), only
present up to know in MPS \needcite what makes the notion of unforgeability more
subtle. The fact that multiple users may produce signatures opening to the same
value necessarily forces to generalize what is a forgery -- and, certainly,
resorting to extraction-based techniques seems unavoidable.

>>>>

\todo{Mention that, in this definition, a credential that does not meet \fissue
  is not considered a forgery unless it is used to produce a signature. This is
  consistent with other works -- e.g., Camenisch, Krenn, Lehmann...}
\todo{Require that $n>=1$ in the creds used to produce a signature...}

@@

\paragraph{On the generality of unforgeability in \UAS schemes.} %
Regarding the information revealed at signature time ($\yeval^0$), \UAS's
unforgeability notion is equivalent to that of known AC schemes. It is the
generalization of the information output at opening time ($\yinsp$), only
present up to know in MPS \cite{ngsy22} what makes the notion of unforgeability
more subtle. The fact that multiple users may produce signatures opening to the
same value necessarily forces to generalize what is a forgery -- and, certainly,
resorting to extraction-based techniques seems unavoidable.
